Internship Summary: Mid-Term Review

### 2020-07-21 RapportStage/Rapport.tex
update tuesday

The eigenvectors associated to the energies \eqref{eq:E_2x2} are
\begin{equation}
\phi_{\pm}=\begin{pmatrix}
\frac{1}{2\lambda}(\epsilon_1 - \epsilon_2 \pm \sqrt{(\epsilon_1 - \epsilon_2)^2 + 4\lambda^2}) \\ 1
\end{pmatrix},
\end{equation}
and for $\lambda=\lambda_\text{EP}$ they become
\begin{equation}
\phi_{\pm}=\begin{pmatrix}
\mp i \\ 1
\end{pmatrix},
\end{equation}
which are clearly self-orthogonal. The equation (7) can be rewrite as
\begin{equation}
\phi_{\pm}=\begin{pmatrix}
\frac{1}{\lambda}(\frac{\epsilon_1 - \epsilon_2}{2} \pm \sqrt{2\lambda_\text{EP}} \sqrt{\lambda - \lambda_\text{EP}}) \\
\end{pmatrix},
\end{equation}
we can see that if we normalise them they will behave as
$(\lambda - \lambda_\text{EP})^{-1/4}$ resulting in the following pattern when looping around one EP:
\begin{align}
	\phi_{\pm}(2\pi) & = \phi_{\mp}(0),
	&
	\phi_{\pm}(4\pi) & = -\phi_{\pm}(0) \\
	\phi_{\pm}(6\pi) & = -\phi_{\mp}(0),
	&
	\phi_{\pm}(8\pi) & = \phi_{\pm}(0),
\end{align}
showing that 4 loops around the EP are necessary to recover the initial state. We can also that looping around the other way round leads to a different pattern.
\titou{Maybe you should add a few equations here to highlight the self-orthogonality process. 
What do you think?
You could also show that the behaviour of the wave function when one follows the complex contour around the EP.}

@@

We obtained the equation \eqref{eq:EUHF} for the general form of the wave function \eqref{eq:UHF_WF}, but to be associated with a physical wave function the energy needs to be stationary with respect to the coefficients. The general method is to use the Hartree-Fock self-consistent field method \cite{SzaboBook} to get the coefficients of the wave functions corresponding to physical solutions. We will work in a minimal basis ($Y_{00}$ and $Y_{10}$) to illustrate the difference between the RHF and UHF solutions. In this basis there is a shortcut to find the stationary solutions. One can define the one-electron wave functions $\phi(\theta)$ using a mixing angle between the two basis functions. Hence we just need to minimize the energy with respect to the two mixing angles $\chi_\alpha$ and $\chi_\beta$.

>>>>

The eigenvectors associated to the energies \eqref{eq:E_2x2} are
\begin{equation}
\phi_{\pm}=\begin{pmatrix}
\frac{1}{2\lambda}(\epsilon_1 - \epsilon_2 \pm \sqrt{(\epsilon_1 - \epsilon_2)^2 + 4\lambda^2}) \\ 1
\end{pmatrix},
\end{equation}
and for $\lambda=\lambda_\text{EP}$ they become
\begin{equation}
\phi_{\pm}=\begin{pmatrix}
\mp i \\ 1
\end{pmatrix},
\end{equation}
which are clearly self-orthogonal. The equation (7) can be rewrite as
\begin{equation}
\phi_{\pm}=\begin{pmatrix}
\frac{1}{\lambda}(\frac{\epsilon_1 - \epsilon_2}{2} \pm \sqrt{2\lambda_\text{EP}} \sqrt{\lambda - \lambda_\text{EP}}) \\ 1
\end{pmatrix},
\end{equation}
we can see that if we normalise them they will behave as
$(\lambda - \lambda_\text{EP})^{-1/4}$ resulting in the following pattern when looping around one EP:
\begin{align}
	\phi_{\pm}(2\pi) & = \phi_{\mp}(0),
	&
	\phi_{\pm}(4\pi) & = -\phi_{\pm}(0) \\
	\phi_{\pm}(6\pi) & = -\phi_{\mp}(0),
	&
	\phi_{\pm}(8\pi) & = \phi_{\pm}(0),
\end{align}
showing that 4 loops around the EP are necessary to recover the initial state. We can also that looping around the other way round leads to a different pattern.
\titou{Maybe you should add a few equations here to highlight the self-orthogonality process. 
What do you think?
You could also show that the behaviour of the wave function when one follows the complex contour around the EP.}

@@

We obtained the equation \eqref{eq:EUHF} for the general form of the wave function \eqref{eq:UHF_WF}, but to be associated with a physical wave function the energy needs to be stationary with respect to the coefficients. The general method is to use the Hartree-Fock self-consistent field method \cite{SzaboBook} to get the coefficients of the wave functions corresponding to physical solutions. We will work in a minimal basis, composed  of a $Y_{00}$ and a $Y_{10}$ spherical harmonic, or equivalently a s and a p\textsubscript{z} orbital, to illustrate the difference between the RHF and UHF solutions. In this basis there is a shortcut to find the stationary solutions. One can define the one-electron wave functions $\phi(\theta)$ using a mixing angle between the two basis functions. Hence we just need to minimize the energy with respect to the two mixing angles $\chi_\alpha$ and $\chi_\beta$.
